Up to date until \monthday{4}{8}.

\begin{logbookTable}{Ivo}
	%\logEntry{Month}{Day}{# minutes}{Description} or
   	%\logEntry[Year (default 2016)]{Month}{Day}{# minutes}{Description}

% Pre-orientation phase
    \logEntry{02}{02}{120}{First group meeting.}
	\logEntry{02}{05}{600}{Finished abstract.}
	\logEntry{02}{12}{140}{Worked on self-reflection.}
    \logEntry{02}{17}{30}{Finished and handed in self-reflection}
    \logSubtotal{Pre-orientation phase}

% Orientation phase
	\logEntry{02}{16}{420}{Worked on the project as a group.}
    \logEntry{02}{16}{60}{Working on personal and group logbook.}
	\logEntry{02}{16}{120}{Prepared presentation about software Validation and Testing.}
	\logEntry{02}{17}{200}{Worked on the project as a group.}
	\logEntry{02}{19}{200}{Worked on the project as a group.}
    \logEntry{02}{19}{60}{Stayed to keep working on the minutes}
    \logEntry{02}{19}{40}{Worked some more on the minutes}
    \logEntry{02}{20}{40}{Finished the minutes of week 2 and informed the group about it.}
    \logEntry{02}{22}{45}{reading things for the presentations and the presentations form the others so far.}
    \logEntry{02}{22}{100}{excluding the UPPAAL part, completed my part of the presentations.}
    \logEntry{02}{22}{50}{worked on the UPPAAL part of the presentation.}
    \logEntry{02}{23}{180}{Meeting with tutor + preparing for presentation + did the midterm presentations.}
    \logSubtotal{Orientation phase}

% Machine design phase
	\logEntry{02}{23}{400}{Worked on the project as a group: Started with the software Specification (finite automaton) + made some changes to the machine design }
    \logEntry{02}{23}{10}{Stayed another 10 min to work a bit on the Finite State Automaton.}
    \logEntry{02}{24}{210}{Worked on the project as a group: Flashing the custom firmware onto the brick (mostly done by Adriaan) + Discussed the machine design deliverable + made some changes to the machine design + making a first build of a complete Finite State Automaton for our sorting machine.}
    \logSubtotal{Machine Design phase}
    
% Software phases
    \logEntry{02}{26}{120}{Worked on the project as a group: Specifying the software structure based on the finite automaton}
    \logEntry{02}{26}{105}{Meeting Training (STU) + Tests of inputs }
    \logEntry{03}{01}{450}{Group meeting/Worked on the project as a group: Worked on the UPPAAL Model and started with Software Design }
    \logEntry{03}{02}{240}{Resumed software design and implementation.}
    \logEntry{03}{04}{210}{Worked on the software implementation of the input and output. (Left a bit earlier then the rest because I had to catch my train.)}
    \logEntry{03}{08}{400}{Meeting with tutor + I updated the minutes + I converted my personal logbook from the informal version in word into the \LaTeX \space file shared on overleaf. }
    \logEntry{03}{09}{230}{Worked on the project as a group}
    \logEntry{03}{15}{450}{Meeting with tutor + Worked on the project as a group. 
    I made the agenda's of this week and the minutes of today. + I wrote UPPAAL queries for verification.}
    \logEntry{03}{15}{30}{Worked on the UPPAAL queries for another 30 min.}
    \logEntry{03}{16}{220}{Group meeting/Worked on the project as a group: Continued working on the software design deliverable / added some pseudo code + tweaked the machine design a little bit + started on system validation and testing.}
    \logEntry{03}{17}{150}{Worked on peer review and System Validation and testing.}
    \logEntry{03}{18}{200}{Worked on System Validation and Testing.}
    \logEntry{03}{19}{90}{worked on System Validation and Testing.}
    \logEntry{03}{22}{30}{Worked 30 min on System Validation and Testing before the meeting.}
    \logEntry{03}{22}{390}{Meeting and worked on the project with the group.}
    \logEntry{03}{22}{200}{Still working on System Validation and Testing.}
    \logEntry{03}{23}{260}{Meeting + I finished documenting my part of System Validation and testing. + updated my logbook.}
    \logEntry{03}{25}{180}{Finished my final self-reflection document.}
    \logEntry{04}{07}{215}{worked on the conclusion of the project file.}
    \logEntry{04}{07}{5}{finalized my logbook.}
    \logSubtotal{Software, verification and completion phases}
    \logTotal
\end{logbookTable}